%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}
%\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
%\usepackage{hyperref}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{outlines}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingOneline}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    #1
  }
}


\renewcommand{\labelitemii}{$\circ$}


\newlist{SubItemList}{itemize}{1}
\setlist[SubItemList]{label={$-$}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Eric Leonardo Lim}} & Email : \href{mailto:elim023@e.ntu.edu.sg}{elim023@e.ntu.edu.sg} \\ 
  952 Jurong West Street 91 \#08-725, Singapore, 640952 & Mobile : +65-8317-5965\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nanyang Technological University}{August 2014 -- May 2018}
      {Bachelor of Engineering (Computer Science) with Minor in Mathematics}{Singapore}
      \begin{outline}
          \1 CGPA: 4.49/5.0
      \end{outline}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Intern}{January 2017 -- May 2017}
      {SAP}{Singapore}
      
      \begin{outline}
         \1 Researched and developed Machine Learning models (NLP/Text-Mining) in Python.
         \vspace{-4pt}
        \end{outline}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheadingOneline{Final Year Project}{August -- May 2018}
        \begin{outline}
        \1 Researched about a summary data structure for graph data stream and implemented in C++.
        \end{outline}
        
  \resumeSubheadingOneline{HiveIO}{February 2018}
        \begin{outline}
        \1 Developed a multi-player tower conquering game from scratch with Python, HTML5, and Javascript at \href{http://hacknroll.nushackers.org/}{NUS Hack N' Roll 2018}.
        \end{outline}

      
    \resumeSubheadingOneline{\href{https://www.kaggle.com/c/quora-question-pairs}{Quora Question Pairs}}{April 2017 -- May 2017}
      
    \begin{outline}
         \1 Participated in a Data Science challenge hosted on Kaggle in which participants are to develop a model that given a dataset that consists of pairs of questions, predicts whether they are essentially just duplicates of one another.
         \vspace{-4pt}
         \1 Developed a custom Bidirectional-LSTM network in Python to solve the challenge.
         \vspace{-4pt}
         \1 Attained a top 25\% place in the final leaderboard.
        \end{outline}
      
    \resumeSubheadingOneline{Multi-Disciplinary Project}{August 2016 -- December 2016}
        \begin{outline}
            \1 Collaborated with 1 Computer Engineering student and 7 Computer Science students to build a maze-solving robot.
            \vspace{-4pt}
            \1 Developed the algorithm of the robot.
        \end{outline}
      
    \resumeSubheadingOneline{Curator}{January 2016 -- April 2016}
      {
        \begin{outline}
         \1 Developed an Android application that provides general information and events of museums in Singapore. The application uses Google Place API.
        \end{outline}
      }
  \resumeSubHeadingListEnd
  
\section{Awards}
  \resumeSubHeadingListStart
    \resumeItem{$2^{nd}$ Place at \href{https://icpc.baylor.edu/regionals/finder/ar-yangon-2017}{The ACM International Collegiate Programming Contest (ICPC) Asia Yangon Regional 2017}}
      {
      \begin{outline}
       \vspace{-4pt}
       \1 Participated in an international team-based 5-hour algorithmic programming contest (in C++) consisted of teams from top universities in West Pacific and South East Asia as participants.
       \vspace{-4pt}
       \1 Topics of problems include dynamic programming, graphs, advanced data structures (e.g. segment tree, fenwick tree), and mathematics.
       \vspace{-4pt}
       \1 Won the 2nd place.
       \vspace{-4pt}
      \end{outline}
      }
  \resumeSubHeadingListEnd

\section{Co-Curricular Activities}
\resumeSubHeadingListStart
    \resumeSubheading
      {Logistics Officer}{August 2015 -- May 2016}
      {NTU Catholic Students Apostolate - Charismatic Prayer Group}{}
        \begin{outline}
         \1 Responsible for event room booking \& preparation.
        \end{outline}
    \resumeSubheading
      {IT Director}{August 2014 -- May 2015}
      {NTU Brainteractive Club}{}
        \begin{outline}
         \vspace{-4pt}
         \1 Built a new website for the club using WordPress.
         \vspace{-4pt}
         \1 Maintained the website.
         \vspace{-4pt}
        \end{outline}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
  \textbf{Languages}{: C++, Python, Java, Javascript, SQL}\\
}
\item{
  \textbf{Technologies}{: Linux, LaTeX, Google Cloud Engine, Jupyter Notebook, Keras, Scikit-Learn, Numpy, Pandas, NLTK, Unity}
}
  \resumeSubHeadingListEnd

\section{Miscellaneous}
\resumeSubHeadingListStart
\item{
  \textbf{Expected salary}{: S\$3800 (Median salary according to Graduate Employment Survey 2017)}\\
}
\item{
  \textbf{Availability to commence work}{: 21 June 2018}
}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
